### 2019-02-15 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Ok code for Chapter:6

%
% Regular plots of centralized regrets
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=1.10\textwidth]{MP__K3_M2_T5000_N1000__4_algos/all_RegretCentralized____env1-1_2643560344649862285.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=1.10\textwidth]{MP__K3_M3_T5000_N1000__4_algos/all_RegretCentralized____env1-1_4683123079851881812.pdf}
    % \end{subfigure}
    \caption[Second failure case of \Selfish]{Regret, $M=2$ and $M=3$ players, $K=3$ arms, horizon $T=5000$, against $1000$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \Selfish{} (top curve in \textcolor{darkgreen}{green}) clearly fails in such setting with small $K$.}
    \label{fig:5:selfish_fail2}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

>>>>

%
% Regular plots of centralized regrets
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=1.00\textwidth]{MP__K3_M2_T5000_N1000__4_algos/all_RegretCentralized____env1-1_2643560344649862285.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=1.00\textwidth]{MP__K3_M3_T5000_N1000__4_algos/all_RegretCentralized____env1-1_4683123079851881812.pdf}
    % \end{subfigure}
    \caption[Second failure case of \Selfish]{Regret, $M=2$ and $M=3$ players, $K=3$ arms, horizon $T=5000$, against $1000$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \Selfish{} (top curve in \textcolor{darkgreen}{green}) clearly fails in such setting with small $K$.}
    \label{fig:5:selfish_fail2}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

### 2019-02-15 2-Chapters/6-Chapter/chapter6.tex
Ok for tex root
It's a really long and booooring work
Okay for chapters and parts
Ok code for Chapter:6

%!TEX root = ../thesis.tex

% First chapter begins here
\chapter{Towards Non-Stationary Models}
\label{chapter:6}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/6-Chapter/Images/}}

This chapter is basically a raw include from my paper ``The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits'', see https://hal.inria.fr/hal-02006471

@@

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter 6}
\label{sec:6:conclusion}

In this chapter, we saw...

Future works include...

>>>>

%!TEX root = ../PhD_thesis__Lilian_Besson

\chapter{Non-Stationary MAB Models and Possible Applications for IoT Networks}
\label{chapter:6}
\minitoc

Abstract for Chapter 6.

\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/6-Chapter/Images/}}

% This chapter is basically a raw include from my paper ``The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits'', see https://hal.inria.fr/hal-02006471

\TODOL{Rewrite and reorder most of this Chapter, with more subsections, less paragraphs etc, and less copy-paste of our paper \cite{Besson2019GLRT}.}

@@

% % ----------------------------------------------------------------------------
% \section{Conclusion of Chapter 6}
% \label{sec:6:conclusion}

% In this chapter, we saw...

% Future works include...
